### 2022-03-08 ch1.tex
even more bib fixes
fix paper 1 tables, finish most of writing
finish paper 1
haven't commited in a while.

This dissertation focuses on how people search for information and how
people rely on this information and other cues to inform their
health-behaviors and develop norms. I will investigate the following
questions:

- How can we operationalize Google Search Trends as a valid indicator for uses in social science research?    
- How do computer-mediated or interpersonal information-seeking strategies vary
across populations?
- What factors lead people to perform health information search on the Covid-19 vaccine online versus among social network ties? 
- How are new health behavior norms regarding public health recommendations formed during the Covid-19 pandemic?  
- How are patterns of information-search related to social norm stabilization during the Covid-19 pandemic?

@@

\emph{need to cite \citep{bayer_etal20, bossetta18}}

@@

@@

@@

@@

From studies of mass communication, uses and gratifications theory (UGT)
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}
may also lend itself to theorizing why
computer-mediated or interpersonal information-seeking strategies vary.
UGT posits that users are not passive consumers of media and that people
have an active role in choosing different sources of media based on
their satisfaction of specific needs on an individual basis. UGT is
based on Maslow's \citeyearpar{maslowTheoryHumanMotivation1943}
hierarchy of needs and is compatible with
Lazarsfeld and Katz's theory of two-step flow because people can choose
their media and the opinion leaders they follow. Modern-day theorists
have extended UGT theory and classified the uses and gratifications of
the internet and of social media. \citet{staffordDeterminingUsesGratifications2004}
theorize that the internet provides gratification through useful content
that meets expectations, gratification from purposeful navigating or
random browsing as a process, and social gratification from forming and
deepening social ties. \citet{leungGenerationalDifferencesContent2013} theorizes that 
social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection,
and fulfills cognitive needs. Adapting UGT to my own purposes, I
theorize that informational support will be activated from network ties
when the informational need is related to forming and deepening social
ties but search will be conducted online when information is needed but
an individual does not have an additional cognitive need to fill through
social interaction. Alternative goals such as identity management or
relational maintenance \citep{brashersInformationSeekingAvoiding2002}
need to be balanced and will determine where search is conducted.

@@

Social norms form the building blocks of social organization and have
been a focus of sociology since the beginning. In a recent Annual Review
of Sociology piece focused on social norms, Horne and Mollborn define
norms as "group-level evaluations of behavior ... [or] when people
have expectations about how others evaluate behaviors" \citeyearpar[p. 468-69]{horneNormsIntegratedFramework2020}. Durkheim saw that society exerted powerful
forces on individuals and classified people's norms, beliefs, and values
as parts of collective consciousness that provide for societal
integration \citep{durkheimDivisionLaborSociety1933, durkheimSuicide1897}.
Weber, on the other hand,
distinguished social behavior from social action, which was an action a
person takes through subjective understanding and interpretation of
actions of others. % TODO CITE ME

The causes and logics of social norms are debated. The consequentialist
argument for norms focuses merely on the consequence a behavior has on
group members and that norms will be promoted if the behavior benefits
others and denounced if it negatively affects others \citep{ullmannmargalitEmergenceNorms1977}.
 While this theory has been tested and performs well in the lab,
researchers have raised questions regarding its ecological validity
\citep{horneNormsIntegratedFramework2020}. One of the main critiques of the
consequentialist argument is that it relies on the same interpretation
by all parties of what is harmful and beneficial -- a critical question
for the research question in Part 4: Paper 3. The Relational argument % TODO ADD LINK
for norms is based on the value people place on their relationships and
the assumption that people will behave in ways that will garner them
positive social reactions. This argument relies on individuals assuming
what their peers will approve and disapprove of. In turn, norms are
developed when individuals make inferences from their social worlds
\citep{fryeCulturalMeaningsAggregation2017}.

@@

@@

\section{Broader Impact}

@@

@@

\subsection{Article 1: Construct Validity and Correspondence of Google Trends}
% TODO Double check name
% TODO link to article  
I will first investigate how Google Search Trends can be operationalized
as cultural attitudes, disease prevalence and voting behaviors through
comparing trends data to observed valid indicators of these cases.
Specifically, I will test cultural indicators from the NORC General
Social Survey, United States county-level suicide rates from National
Center for Health Statistics, US case rates of Covid-19 from The New
York Times, historical US Presidential Election results, and the
American National Election Survey against selected Google Trends terms
and analyze the data using correlation methods. The aim of this article
is to assess the construct validity and will contribute to critical big
data studies and sociological methodology.
% TODO ADD IN ARTICLE 1 ABSTRACT

\subsection{Article 2: Information-Seeking Behaviors for Information on Covid-19 Vaccinations}
% TODO Double check name
% TODO link to article  
The second article in my dissertation investigates the question "what
are the behavioral processes that lead to macro-level outcomes" (in this
case, Google Trends results) proposed by \citet{breigerScaling2015}. Knowing that
Google trends data only encompasses a small portion of the
information-seeking done by modern humans, it is important to
investigate what leads individuals to search for a question online using
a search engine (contributing to macro-level trends data) versus more
traditional means of information gathering, such as network activation
(asking someone in their social network for informational support). To
investigate this, I use the case of receiving, requesting, and sharing
information about the Covid-19 vaccine in a survey I received funding to
conduct of 900 Adults in the United States.

@@

\subsection{Article 3: Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}
% TODO Double check name
% TODO link to article  
My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty using the
cases of both a) population mobility during early 2020 and b)
vaccination rates during early 2021, both as responses to public health
recommendations to mitigate the Covid-19 pandemic. Using theories of
associative diffusion and the integrated theoretical framework of norms,
I test how these health behaviors are outcomes of assortative signaling
from networks and other sources, such as social isolation and connection
between communities, religious and political conservativism, and
attention to media sources, and online norms as measured by
information-search behaviors. To investigate this, I conduct statistical
modelling on a dataset I compiled from multiple sources, including
Google, Facebook, and the Center for Disease Control and Prevention.

>>>>

\begin{center}
    \texttt{UNDERGOING CHANGES}
\end{center}

This dissertation focuses on how people search for information and how
people rely on this information and to inform their
health-behaviors and develop norms. I will investigate the following
questions:

@@

\citep{sparrow2011google} - memory is worse, reliance on technology

\section{Background}

\subsection{Information Flow}

@@

\subsection{Information Search in The Digital Age}
computer-mediated information search - as in the pre-internet age, you could find information without asking a friend or an expert. encyclopedias.. etc.

computer mediated communication

Social media...  \citep{bayer_etal20}
"“Social media are Internet-based, disentrained, and persistent channels of
masspersonal communication facilitating perceptions of interactions 
among users, deriving value primarily from user-generated content.” \citep[][p. 50]{carr2015social}

Social Networking Site - profile, stream , network, messaging \citep{boyd2007social, ellison2013sociality}

integration of the one-to-one communication formations (face-to-face, letters, texting) within the context of one-to-many forms of communication (television, radio) \citep{o2018masspersonal}

\subsection{Theory of Uncertainty Management}

@@

\citep{sparrow2011google} - memory is worse, reliance on technology

\subsection{Social Support}

@@

% TODO where to put this?
Indeed, much research has revealed the higher levels of social capital of Facebook users \citep{liu2016meta}, with findings indicating that using SNSs to find information and relationship maintenance indicating the highest levels of bridging capital.

@@

From studies of mass communication, uses and gratifications theory (UGT)
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}
may also lend itself to theorizing why
computer-mediated or interpersonal information-seeking strategies vary.
UGT posits that users are not passive consumers of media and that people
have an active role in choosing different sources of media based on
their satisfaction of specific needs on an individual basis. UGT is
based on Maslow's \citeyearpar{maslowTheoryHumanMotivation1943}
hierarchy of needs and is compatible with
Lazarsfeld and Katz's theory of two-step flow because people can choose
their media and the opinion leaders they follow. Modern-day theorists
have extended UGT theory and classified the uses and gratifications of
the internet and of social media. \citet{staffordDeterminingUsesGratifications2004}
theorize that the internet provides gratification through useful content
that meets expectations, gratification from purposeful navigating or
random browsing as a process, and social gratification from forming and
deepening social ties. \citet{leungGenerationalDifferencesContent2013} theorizes that 
social media is gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection,
and fulfills cognitive needs. Adapting UGT to my own purposes, I
theorize that informational support will be activated from network ties
when the informational need is related to forming and deepening social
ties \citep{baumeister,grieve2013face} but search will be conducted online when 
information is needed but
an individual does not have an additional cognitive need to fill through
social interaction. Alternative goals such as identity management or
relational maintenance \citep{brashersInformationSeekingAvoiding2002}
need to be balanced and will determine where search is conducted.

\subsection{new literature to add}

\citet{bayer_etal20}
profiles and self-presentation
networks and social mobilization
streams and social comparison
messages and social connectedness

\citet{bossetta18}
"tools that are easy to use and functional to the demands of varying using demographics"
"digital architecture - the technical protocols that enable, constrain and shape user behavior in a virtual space"
Different platforms deliver different user experiences along the dimensions of searchability, connectivity, and privacy

\citet{boyd2010social}
"Networked publics serve many of the same functions as other types of publics – they allow people to gather for social, cultural, and civic purposes and they help people connect with a world beyond their close friends and family. " p 39
• Persistence: online expressions are automatically recorded and archived
• Replicability: content made out of bits can be duplicated.
• Scalability: the potential visibility of content in networked publics is great.
• Searchability: content in networked publics can be accessed through search

@@

Social norms form the building blocks of social organization and have
been a focus of sociology since the beginning. In a recent Annual Review
of Sociology piece focused on social norms, Horne and Mollborn define
norms as "group-level evaluations of behavior ... [or] when people
have expectations about how others evaluate behaviors" \citeyearpar[p. 468-69]{horneNormsIntegratedFramework2020}. Durkheim saw that society exerted powerful
forces on individuals and classified people's norms, beliefs, and values
as parts of collective consciousness that provide for societal
integration \citep{durkheimDivisionLaborSociety1933, durkheimSuicide1897}.
Weber, on the other hand, distinguished social behavior from social action,
which was an action a person takes through subjective understanding and
interpretation of actions of others \citep{weber1978economy}.

The causes and logics of social norms are debated. The consequentialist
argument for norms focuses merely on the consequence a behavior has on
group members and that norms will be promoted if the behavior benefits
others and denounced if it negatively affects others \citep{ullmannmargalitEmergenceNorms1977}.
 While this theory has been tested and performs well in the lab,
researchers have raised questions regarding its ecological validity
\citep{horneNormsIntegratedFramework2020}. One of the main critiques of the
consequentialist argument is that it relies on the same interpretation
by all parties of what is harmful and beneficial -- a critical question
for the research question in \hyperlink{paper-3}{Paper 3}. The Relational argument 
% TODO check if link works
for norms is based on the value people place on their relationships and
the assumption that people will behave in ways that will garner them
positive social reactions. This argument relies on individuals assuming
what their peers will approve and disapprove of. In turn, norms are
developed when individuals make inferences from their social worlds
\citep{fryeCulturalMeaningsAggregation2017}.

@@

\subsection{Social Networks}

@@

\section{Broader Impact}
\begin{center}
    \texttt{UNDERGOING CHANGES}
\end{center}

@@

\begin{center}
    \texttt{all three of these are UNDERGOING CHANGES}
\end{center}

\begin{figure}
{\centering \includegraphics[width=\linewidth]{figs/ch1/Dissertation Concept Map - Color.pdf}}
\caption{Theoretical Framework for the Dissertation}\label{fig:concept-map}
\end{figure}

@@

% TODO integrate research questions
- How can we operationalize Google Search Trends as a valid indicator for uses in social science research?    
- How do computer-mediated or interpersonal information-seeking strategies vary
across populations?
- What factors lead people to perform health information search on the Covid-19 vaccine online versus among social network ties? 
- How are new health behavior norms regarding public health recommendations formed during the Covid-19 pandemic?  
- How are patterns of information-search related to social norm stabilization during the Covid-19 pandemic?

\subsection{Article 1: Construct Validity and Correspondence of Google Trends}
% TODO Double check name
% TODO link to article

\hyperlink{paper-1}{Paper 1}
I will first investigate how Google Search Trends can be operationalized
as cultural attitudes, disease prevalence and voting behaviors through
comparing trends data to observed valid indicators of these cases.
Specifically, I will test cultural indicators from the NORC General
Social Survey, United States county-level suicide rates from National
Center for Health Statistics, US case rates of Covid-19 from The New
York Times, historical US Presidential Election results, and the
American National Election Survey against selected Google Trends terms
and analyze the data using correlation methods. The aim of this article
is to assess the construct validity and will contribute to critical big
data studies and sociological methodology.
% TODO ADD IN ARTICLE 1 ABSTRACT

\subsection{Article 2: Information-Seeking Behaviors for Information on Covid-19 Vaccinations}
% TODO Double check name
% TODO link to article  
\hyperlink{paper-2}{Paper 2}
The second article in my dissertation investigates the question "what
are the behavioral processes that lead to macro-level outcomes" (in this
case, Google Trends results) proposed by \citet{breigerScaling2015}. Knowing that
Google trends data only encompasses a small portion of the
information-seeking done by modern humans, it is important to
investigate what leads individuals to search for a question online using
a search engine (contributing to macro-level trends data) versus more
traditional means of information gathering, such as network activation
(asking someone in their social network for informational support). To
investigate this, I use the case of receiving, requesting, and sharing
information about the Covid-19 vaccine in a survey I received funding to
conduct of 900 Adults in the United States.

@@

\subsection{Article 3: Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}
% TODO Double check name
% TODO link to article  
\hyperlink{paper-3}{Paper 3}

My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty using the
cases of both a) population mobility during early 2020 and b)
vaccination rates during early 2021, both as responses to public health
recommendations to mitigate the Covid-19 pandemic. Using theories of
associative diffusion and the integrated theoretical framework of norms,
I test how these health behaviors are outcomes of assortative signaling
from networks and other sources, such as social isolation and connection
between communities, religious and political conservativism, and
attention to media sources, and online norms as measured by
information-search behaviors. To investigate this, I conduct statistical
modelling on a dataset I compiled from multiple sources, including
Google, Facebook, and the Center for Disease Control and Prevention.
